{\small Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}

### 2017-11-13 Meetings/GPMNov2017/gpm_november2017_topic21.tex
updte
Update to slides which a first possible version

\begin{frame}{LSN \textit{vs} Double null on TCV}
%  \begin{columns}
%    \begin{column}{0.5\textwidth}
      \centering{\includegraphics<1>[width=.6\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesLSN-DN}}
      \centering{\includegraphics<2>[width=.8\textwidth]{../../Experiments/TCV/analysis/pdfbox/DNRadiation_58623}}
      \centering{\includegraphics<3>[width=.8\textwidth]{../../Experiments/TCV/analysis/pdfbox/DNRadiation_58624}}
      \centering{\includegraphics<4>[width=.8\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeLSN-DN}}
%    \end{column}
%    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \item<1|only@1> Comparing similar L-Mode density ramp at same
          current in LSN and DN with ion $\mathbf{B}\times\nabla B$
          pointing towards the floor. Lower ion flux to lower target
          observed in DN and profiles before rollover seem more broad
          in LSN. After rollover the profiles are actually similar
      \item<2|only@2>  From bolometry we can observe an
          unbalanced movement of the radiation front suggesting a non
          perfectly balanced DN
      \item<3|only@3> This is confirmed at higher current where the
        more active X-point is the upper one with a consequent higher
        radiation from bolometry chords    
      \end{itemize}
%    \end{column}
%  \end{columns}
\end{frame}

@@

\begin{frame}{Comments on different divertor geometry}

\end{frame}

\begin{frame}{Program for 2018: AUG}
  \begin{itemize}
     \item X-point manipulator (NPH ?) simultaneously with MEM
     \item X-point vertical shift in order to have SP at different
	vertical height at the target. \alert{We will observe similar
          observation as obtained in JET when moving from horizontal
          to vertical target?}
     \item DN discharges. With slow movement of the second X-point into the vessel
	to be performed at constant power/density where shoulder
        alreay exists. \alert{This is mandatory to complement the
          information obtained on TCV}
     \item USN with midplane/X-point manipulator to monitor the
       upstream SOL 
\item
\end{itemize}
 \end{frame}
 \begin{frame}{MST2-NPH}
   \begin{columns}
     \begin{column}{0.5\textwidth}
       \centering{\includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NPH_2018}}
     \end{column}
     \begin{column}{0.5\textwidth}
       \begin{itemize}
         \item MST2 founded project for the realization of a New Probe
           Head (NPH) (C. Ionita,  B. Schneider \textit{et al})
         \item Simultaneous information on Ion temperature (2 RFAs),
           Plasma potential and electron temperature (Emissive probe
           coupled with floating potential) and magnetic fluctuations
           from 2 3-axial magnetic pick up coil
         \item Potentially tested on TCV beginning of 2018 and then
           moved to other MST1 devices
         \item Heat load
       \end{itemize}
     \end{column}
   \end{columns}

 \end{frame}

@@

\begin{frame}{Code requirements}
  \begin{itemize}
    \item Dedicated simulations with first principles codes (GBS,
      HESEL)
    \item Check if trends can be reproduced
    \item potential input for future experiments regarding role of
        f.x. neutrals and recycling
  \end{itemize}
\end{frame}

%\begin{frame}{Outline}
% 	\begin{itemize}
% 		\item Background 
% 		\item Plans (we will not make a detailed list of the
%                   proposal, we already tried to combine and summarize them)
% 		\item Discussion
% 	\end{itemize}	
% \end{frame}

% \section{Background}
% \begin{frame}{Present status}
%   \setbeamercovered{transparent}
%   \begin{enumerate}[<+(1) | invisible@-+>]
%     \item Experimental and theoretical investigations suggest that SOL density profiles are
%       determined by the balance between radial filamentary transport and parallel dynamics
%     \item The balance changes at high density and leads to broadened SOL density profiles $\rightarrow$ \emph{shoulder formation}
%     \item This is observed in L-mode plasmas in a variety of devices including AUG \parencite{Carralero:2014gs},
%       TCV \parencite{Garcia:2007p2615} and MAST \parencite{Militello:2016hk}
%     \item Observations exhibit various other dependencies e.g., divertor
%       collisionality, plasma current, seeding. \alert{Results from
%         different devices not fully reconciled and the underlying mechanism is not fully understood.}
%     \item Studies of shoulder formation in H-Mode are so far limited 
% 	%\item Particle and energy transport in the SOL is crucial for lifetime of PFC in ITER and DEMO
% %    \item First we will report a summary of the achievements and then
%  %    personal comments and plans
%     \end{enumerate}
% \end{frame}
% \section{L-Mode}
% \begin{frame}{L-Mode studies: AUG/1}
%   \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item<1-> AUG and JET \parencite{Carralero:2015gu} suggest that divertor collisionality 
%         \begin{equation*}
%         \Lambda_{div} = \frac{L_{\parallel}/c_s}{1/\nu_{ei}}\frac{\Omega_i}{\Omega_e}
%       \end{equation*}
%       controls filaments size
%         \item<2-> \textcolor{red}{Tested by changing n$_e$
%             and $T_e$ through fueling/seeding/heating}
%         \item<3-> This determines a change of the velocity-size
%           scaling from
%             \textcolor{ta3chameleon}{sheath-limited}
%         to \textcolor{blue}{inertial regime}.
%        \onslide<4->{\alert{$\Lambda_{div}$ rules the density profile scale
%            length}}
%        \item<5> This finally determines the shoulder formation
%         \end{itemize}
%     \end{column}
%     \begin{column}{0.5\textwidth}
%       \only<1-2>{
%       \begin{tikzonimage}[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroPRL15a}
%           \draw [thick, ta3chameleon, thick, rotate=1] (0.43,0.25) ellipse (0.23 and 0.1);
%           \draw [thick, blue, thick, rotate=-4] (0.8,0.55) ellipse (0.1 and 0.33);
%         \only<2>{
%           \draw [ultra thick, red, thick, dashed] (0.5,0.63) circle (0.12);
%         }
%       \end{tikzonimage}}
%     \only<3-4>{
%       \begin{tikzonimage}[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroPRL15b}
%           \draw [ultra thick, ta3chameleon, rotate=1] (0.2,0.5) ellipse (0.05 and 0.4);
%           \draw [thick, blue, rotate=15] (0.65,0.07) ellipse (0.4 and 0.1);
%       \end{tikzonimage}
%     }
%     \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroPRL15c}
%     \end{column}
%   \end{columns}
% \end{frame}

% \begin{frame}{L-Mode studies: AUG/2}
%   \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item<1-> Profile modified by an increase of blob-size and change of
%         \alert{packing fraction: $f_{fil} = \nu_{fil}\tau_{AC}$}
%         \onslide<2->{\textcolor{blue}{and filament relative density}
%           {\footnotesize (Carralero 2016 in preparation)}}
%       \item<3-> As a consequence the contribution of filaments to
%         radial transport increases
%       \item<4|only@4> \alert{Beware the change of frequency may be due to a
%         modification of fluctuation velocity which is known to vary
%         with densities ad normalized greenwald fraction \parencite{0029-5515-51-5-053020}}  
%       \item<5> Parallel flow is strongly reduced whenever we increase
%         the divertor collisionality
%       \end{itemize}
%     \end{column}
%       \begin{column}{0.5\textwidth}
%         \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16a}
%         \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16b}
%         \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16c}
%         \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/AgostiniNF2011}
%         \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16d}
%       \end{column}
%     \end{columns}
%   \end{frame}

%   \begin{frame}{L-Mode studies:AUG/3}
%   \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item<1-> Electron and ions behave differently
%       \item<2|only@2> T$_{e, fil} \sim 1.2 $T$_{e, bk}$ roughly constant
%         accross the SOL and slightly affected by the increase of
%         divertor collisionality
%       \item<3|only@3> Ions are strongly affected: for
%         \textcolor{red}{$\Lambda_{div}<1$ T$_{i, fil} > $ T$_{i, bk}$
%           and $\lambda_{T_i} \sim 30$
%           mm}. \textcolor{blue}{$\Lambda_{div}>1$ T$_{i, fil} \sim $
%           T$_{i, bk}\sim 25$ eV
%           and $\lambda_{T_i} \sim 8$ mm}
%        \item<4-> Ion energy spectrum from
%          $\mathbf{E}\times\mathbf{B}$ analyzer shrinks towards lower
%          energy for $\Lambda_{div} > 1$
%        \item<5> EMC3-Eirene simulation suggests that such a reduction
%          can't be accounted for thermalization process. An
%          \alert{ionization front builds in front of the limiter shadow}   
%        \end{itemize}
%     \end{column}
%       \begin{column}{0.5\textwidth}
%         \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16e}
%         \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16f}
%         \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16g}
%         \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16h}
%       \end{column}
%     \end{columns}
%   \end{frame}

%   \begin{frame}{L-Mode: TCV}
%     \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item<1|only@1> Flexibility has allowed to test $\Lambda_{div}$
%         dependence on L$_{\parallel}$ by varying flux expansion f$_x$:
%         \begin{equation*}
%           f_x = \frac{(B_p/B_t)_{MP}}{(B_p/B_t)_{SP}}
%         \end{equation*}
%         in ohmic density ramps \parencite{vianello:iaea2016}
%       \item<2|only@2> Slight variation of density profiles at the target but
%         due to direct dependence on L$_{\parallel}$ large increase of
%         $\Lambda_{div}$. \alert{Upstream profiles only varies whenever
%         we reach a certain amount of $\langle n_e \rangle$}
%        \only<3-5>{\item Weak dependence of blob-size from $\Lambda_{div}$,
%         \onslide<4-5>{\textcolor{red}{also on a statistical
%             basis}}. \onslide<5>{Strong dependence on average density,
%           independent of L$_{\parallel}$}}
%        \item<6|only@6> $\lambda_n$ depends clearly on blob-size
%          whereas the dependence on divertor condition is less
%          obvious. \alert{$\Lambda_{div}$ necessary but not sufficient}
%       \end{itemize}
%     \end{column}
%       \begin{column}{0.5\textwidth}
%         \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16a}
%         \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16b}
%         \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16c}
%         \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16d}
%         \includegraphics<6>[width=\textwidth]{../../pdfbox/KoM15Nov/VianelloIAEA16e}
%       \end{column}
%     \end{columns}
%   \end{frame}

%   \begin{frame}{L-Mode: JET}
%     \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item<1|only@1> The shoulder formation strongly depends on
%         divertor geometry, disappear with vertical target and strike
%         point closest to cryogenics pumps \parencite{Wynn:EPS2016}
%       \item<2|only@2> The midplane pressure from baratrons is
%         equivalent between the different divertor. \alert{This would
%           indicate that SOL neutral density at the outboard midplane does not play any role}
%        \item<3|only@3> In the horizontal target configuration the
%          results indicate that the shoulder forms right at the
%          transition from sheath-limited to high-recycling where also
%          $\Lambda_{div}$ strongly increase
%        \item<4|only@4> Shoulder amplitude correlates with strike
%          points position. \alert{Shoulder, ionization and
%            $\Gamma_{ion, plate}$ larger when R$_{strike}$ smaller away
%          from the pump}
%        \item<5|only@5> In seeded discharges the transition observed at
%          very high level of $\Lambda_{div} >> 1$
%       \end{itemize}
%     \end{column}
%       \begin{column}{0.5\textwidth}
%         \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16a}
%         \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16b}
%         \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16c}
%         \includegraphics<4>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16d}
%         \includegraphics<5>[width=\textwidth]{../../pdfbox/KoM15Nov/LipschultzITPA16e}
%       \end{column}
%     \end{columns}
%   \end{frame}

%   \begin{frame}{L-Mode: MAST}
%     \begin{columns}
%     \begin{column}{0.5\textwidth}
%       \begin{itemize}
%       \item<1|only@1> Strong dependence on
%         I$_p$ \parencite{Militello:2016hk}. Increasing I$_p$ at
%         constant toroidal field shoulder disappears. Consistent with
%         observation in other devices
%       \item<2|only@2> Filaments binormal dimension increases with
%         current \parencite{Kirk:2016jj} or equivalently decreases with L$_{\parallel}$
%        \item<3|only@3> Filament radial velocity decreases with current
%          as well as the radial dimension \parencite{Kirk:2016jj}
%       \end{itemize}
%     \end{column}
%       \begin{column}{0.5\textwidth}
%         \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/MilitelloNF16a}
%         \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/KirkPPCF16a}
%         \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/KirkPPCF16c}
%       \end{column}
%     \end{columns}
%   \end{frame}

%   \section{H-Mode}
%   \begin{frame}{AUG: H-Mode}
%     \begin{columns}
%     \begin{column}{0.4\textwidth}
%       \begin{itemize}
%       \item<1|only@1> SOL profiles in H-Mode so far investigated on
%         AUG \parencite{Muller:2015jt,Sun:2015bu,carralero:psi2016}
%       \item<2|only@2> Differently from L-Mode, complete detachment
%         suggested to be mandatory for increasing of $\lambda_n$ \parencite{Sun:2015bu}
%        \item<3|only@3> In weak H-Mode \parencite{carralero:psi2016}
%          shoulder depends on a combination of $\Lambda_{div}$ and
%          fueling rate. Complete detachment seems instead not necessary
%          although very weak shoulder
%       \end{itemize}
%     \end{column}
%       \begin{column}{0.6\textwidth}
%         \includegraphics<1>[width=\textwidth]{../../pdfbox/KoM15Nov/MuellerJNM15a}
%         \includegraphics<2>[width=\textwidth]{../../pdfbox/KoM15Nov/SunPPCF15a}
%         \includegraphics<3>[width=\textwidth]{../../pdfbox/KoM15Nov/CarraleroMST16i}
%       \end{column}
%     \end{columns}
%   \end{frame}

%   \section{Open issues}
%   \begin{frame}{Open and unresolved issues}
%   \setbeamercovered{transparent}
%   \begin{enumerate}[<+(1) | invisible@-+>]
%     \item Does $\Lambda_{div}$ unify the picture among the devices?
%       \alert{No, does neutral pressure play a role?}
%     \item If neutrals play a role is it at the divertor and/or at the midplane?
%       \alert{Contradictory results if one include experiments with
%         midplane puffing, JET and EIRENE simulations}
%     \item Does L$_\parallel$ play any role? \alert{So far TCV suggests no
%       dependence from f$_x$ scan but both TCV and MAST observe an
%       I$_p$ dependence. MAST clearly state filament $\sigma_{\perp}$
%       increases with L$_{\parallel}$ }
%     \item Is cooling the divertor with fueling or seeding equivalent? \alert{Contradictory observations in AUG and JET}
%     \item Do we observe same behavior in L and H-Mode? \alert{So
%       far no as shown in H-Mode AUG. We need higher detachment
%       condition and we need enough fueling}
%       \item Is the density shoulder accompanied with an ion temperature shoulder?
% %      \item What are the underlying mechanisms? 
%     \end{enumerate}
%   \end{frame}

% \section{Topic 21 experiments }
% \begin{frame}{$n_{\text{proposed shots}} \gg n_{\text{allocated shots}}$}
% 	\begin{itemize}
% 		\item 15 were proposals submitted to Topic 21
% 		\item Proposals include experiments on all three machines 
% 		\item There are overlaps between several of the proposals 
% 		\item Preliminary shot allocation. AUG: 14. MAST: 13. TCV: 23 
% 		\item However, total number of proposed shots:  \textbf{449}
% 		\item Several of the proposed experiments can be combined. \underline{But we must prioritize}
% 		\item Reaching all goals is not possible with the current number of allocated shots.
% 	\end{itemize}
% \end{frame}

% \begin{frame}{Focal points}
% \begin{itemize}
% 	\item MST1 uniquely facilitates cross comparison between machines
% 	\item Several of the proposed experiments overlap and will be combined
% 	\item A cross machine experiment has the makings of settling open issues
% 	\item Therefore, we will allocate shots for cross-machine
%           comparison but we must strive after similar machine configuration
% 	\item ....but also to other proposed experiments
% 	\item Cross machine L-mode experiments: 
% 	\begin{enumerate}
% 		\item Investigate the role of neutrals 
% 		\item $I_p$ and $q_{95}$ scans
% 	\end{enumerate}
% 	\item Cross machine H-mode experiments. 
% \end{itemize}	
% \end{frame}

% \begin{frame}{L-mode experiments}
% 	\begin{itemize}
% 		\item The role of neutrals in the shoulder
%                   formation is not understood
%                   {\scriptsize(proponents: Carralero (\# 7), Militello
%                     (\# 1, 2), Vianello (\# 13), Walkden (\# 9))}
% 		\begin{enumerate}
% 		\item We envisage to measure neutral gas profiles at the outboard midplane
%                   using fast cameras with D$_{\alpha}$ filter, density
%                   and temperature SOL profiles and appropriate code
%                   (e.g. KN1D as in \parencite{Lipschultz:2005gg,Lipschultz:2016vk})
% 		\item Reciprocating probes and profiles available on
%                   all machines
%                 \item Investigate role of fueling location (MAST)
% 		\end{enumerate}
% 		\item Disentangle the roles of $I_p$, $q_{95}$, and $L_{\|}$.
%                   {\scriptsize(proponents: Carralero , Militello, Vianello, Tsui, Carralero (\# 7), Militello
%                     (\# 1, 2), Vianello (\# 13), Walkden (\# 9), Tsui
%                     (\# 15))}
% 		\begin{enumerate}
% 			\item Carry out parameter scans on all machines

% 		\end{enumerate}
% 	\end{itemize}
% \end{frame}

% \begin{frame}{H-mode experiments}
% \begin{itemize}
% 	\item ITER and DEMO will operate in H-mode
% 	\item We must know what parameters control shoulder formation 
% 	\item Shoulder formation parameter regime is unclear on all machines
% 	\item Main priorities: 
% 	\begin{enumerate}
% 		\item Investigate if clear shoulder formation exists and what plasma parameters required? 
% 		\item Investigate the SOL (filamentary) transport properties.
%                   Whenever main diagnostic is reciprocating probes $\rightarrow$ limits heating power
% 		\item Experiments must gradually increase power and density. 
% 	\end{enumerate}
% 	\item Fueling in H-mode is problematic due to transport
%           barrier. Is there a way to overcome it? NBI, pellet fueling?
% 	\item H-mode density limit \parencite{Bernert:2015bq} must be dealt with
% \end{itemize}

% \end{frame}

% \begin{frame}{Optimizing cross machine comparison}
% \begin{itemize}
% 	\item Machines are fundamentally differently designed
% 	\item Strive for similar configurations of the machines:
% 	\begin{enumerate} 
% 		\item Single-Null
% 		\item $\bm{B} \times \nabla B$ towards active divertor 
% 		\item Strike-point and cryo pump location (AUG and MAST-U)
% 		\item Heating 
% 		\item Fueling location 
% 		\item Seeding (species, location, rate)
% 	\end{enumerate}
% \end{itemize} 
% %things we cannot influence but could be important : wall (carbon, tungsten), helicity, aspect ratio, divertor design,

% \end{frame}

% \begin{frame}{Required diagnostics and competences}
% In order to compare experiments the following diagnostics must be available: 
% \begin{enumerate}
% 	\item Filaments analysis in the Outboard midplane: 
% 	\begin{itemize} 
% 		\item Through Reciprocating probe then $I_{sat}$  on minimum three pins poloidally and radially separated
% 		 (filaments speed and size). 
% 		\item Electron temperature (fast T$_e$ measurements
%                   can be achieved with BPP in MAST-U {\footnotesize
%                     (N. Walkden \#11)})
% 		\item If possible $M_{\|}$
% 	 \end{itemize}
% 	 \item Camera viewing OM for measuring neutrals 
% 	 \item Divertor measurements of $n$ and $T_e$ (probes) plus
%            spectroscopy and bolometry 
% 	 \item Density profile measurements (Li-Bes, Reflectometry (\#
%            6 Acquiam, \# 8 Vicente), Edge Thomson scattering) 
%          \item Sami and Field for fast particles accelleration (piggy
%            back on developed scenarion \# 4 McClements)
% %	\item H-mode quality diagnostics(div current, magnetics)
% \end{enumerate}
% \end{frame}

% \begin{frame}[allowframebreaks]{Proposed shot plan - AUG}
% \vspace{-1cm}
% Allocated shots $\sim$ 14 + contingency 
% \begin{itemize}
% 	\item L-Mode (6 shots)
% 	\begin{enumerate}
% 		\item Reference shot \# 30276
% 		\item Perform $I_p$ scan (three values) with fixed $B_T$
% 		\item Perform $I_p$ scan fixing  $q_{95}$	 ($B_T$)	
% 		\item $B_T= 2.0$ required by proposal 6 (Aguiam). Should be possible for some shots? 		
% 		\item should we add OM puff to validate neutral measurements?
% 		\item Possibility of strike-point sweeping during shot
% 		\item RFEA measurements in internal program. 
% 		\item These shots combines experiments proposed by:
%                   Carralero (\# 7), Militello (\#1), Vianello (\#13)

% 	\end{enumerate}
% 	\item H-mode (9 shots)
% 	\begin{enumerate}
% 		\item Reference shot \# 33059 (AUG15-2.2-3). Aim is to achieve conditions
%                   in \# 31607 (Sun 6 MW) through careful power and density ramp monitoring new HHF probe 
% 		\item With clear shoulder formation repeat with midplane probe at varying radial positions 
% 		\item Strike-point sweep if feasible? 
% 		\item In all shots, particle acceleration in ELMs will be studied using microwaves,
%                   soft X-rays, and FILD 
% 		\item Reflectometry measurements of density profiles and fluctuations at multiple poloidal locations (Aguiam and Vicente)
% 		\item These shots combine experiments proposed by:
%                   Aguiam (\#6), Carralero (\#7), McClements (\#4),
%                   Militello (\# 1, 2), Vianello (\#13), Vicente (\#8)

% 	\end{enumerate}
% \end{itemize}
% \end{frame}

% \begin{frame}{Proposed shot plan - TCV}
% 	\begin{itemize}
% 		\item L-mode (11 shots)
% 		\begin{enumerate}
% 			\item Reference shot \# 53514
% 			\item Same $I_p$ and $q_{95}$ scans as on AUG
% 			\item Two shots with reversed $\bm{B} \times \nabla B$
% 			\item Move plasma vertically. Disentangle
%                           $q_{95}$ and $L_{\|}$	
%                         \item These shots combines proposal: Vianello
%                           (\#13), Tsui (\#15), Militello (\#1, 2)
% 		\end{enumerate}
% 		\item H-mode (12 shots)
% 		\begin{enumerate}
% 			\item Reference shot \# 53352
% 			\item Since H-mode shoulder is new territory on TCV first shots will be scenario development
% 			\item As on AUG. Incremental increases of power and density. Close monitoring the midplane probe. 
%                         \item These shots combines proposal: Vianello
%                           (\#13), Tsui (\#15), Militello (\#1, 2)
% 		\end{enumerate}
% 	\end{itemize}
% \end{frame}

% \begin{frame}{Preliminary shot plan  - MAST-U}
% 	\begin{itemize}
% 		\item L-mode (6 shots)
% 		\begin{enumerate}		
% 			\item New machine. No reference shot yet			
% 			\item Same $I_p$ and $q_95$ scan to allow
%                           cross-machine comparison. Availability of multi pin probe? 
% 			\item Try varying fueling location
% 			\item RFEA measurements during shoulder
%                           formation 
%                         \item These shots combines proposal: Militello
%                           (\#1, 2, 3), Walkden (\#11), Vianello (\#13)
% 		\end{enumerate}
% 		\item H-mode (7 shots)
% 		\begin{enumerate}
% 			\item These experiments require the existence of H-mode reference shot. Perhaps not available in 2017
% 			\item Similar scenario development as on other emachines
%                         \item These shots combines proposal: Militello
%                           (\#1, 2, 3),  Vianello (\#13)
% 		\end{enumerate}
% 		\item Probe head must be changed to allow
%                   investigation of both fast T$_e$ (BPP),  and T$_i$
%                   (RFEA) but this require careful schedule of machine time
% 	\end{itemize}
% \end{frame}

% \begin{frame}{COMPASS collaboration}
% \begin{itemize}
% \item COMPASS is not an MST1 device, therefore no operational cost
%   will be provided by MST1
% \item However GA agrees that MST1 can provide part of the ppy for
%   running experiments in line with MST1 topics
% \item Proposal \# 14 is focused filaments dynamics and shoulder
%   formation both in L and H-Mode
% \item Experimental plan can be therefore agreed in order to perform
%   similar experiments (e.g. I$_p$ and $q_{95}$ scan in L-Mode)
%   ensuring proper comparison between devices
% \item COMPASS suppose 3ppy for running and evaluation of experiment
%   pertaining Topic-21, among Czeck and other european laboratories.
% \end{itemize}
% \end{frame}

% \begin{frame}{There are urgent experiment which cannot be addressed}
% \begin{itemize}
% 	\item Detailed ion temp measurements. Must eventually be
%           completed in internal programs. Are you willing to share the
%           information among Topic 21 even though done internally?
% 	\item Topology investigations? For example the comparison
%           USN/LSN/DN is not included. Diagnostic capability of upper
%           divertor is weaker than the lower one.
%           Better to use reverse B$_t$  which is known
%           to have influences in detachment as
%           well \parencite{McLean}
% 	\item Strikepoint sweeping and cryo pump
% 	\item Parameters scans in H-mode
% 	\item X-point probes
% \end{itemize}
% \end{frame}

% \begin{frame}{Modeling require}
%   \begin{enumerate}
%     \item Mean field modeling, in particular for neutral investigation.
%       Available for AUG (EMC3-EIRENCE) and
%       MAST-U (SOLPS). So far we lack investigation for these scenario
%       targeting TCV. Manpower needed from edge and SOL modeling
%     \item Turbulence code: we should need self-consistent interaction
%       with neutrals. Possible tools \texttt{BOUT ++}, \texttt{HESEL},
%       \texttt{GBS}, \texttt{Tokam-3X}.
%       Some of them can be run by people who will, very
%       likely, apply for this topic, some other not
%   \end{enumerate}
% \end{frame}

% \begin{frame}{Future and Miscellaneous}
% 	\begin{itemize}
% 		\item Possibility to piggybag on
%                   Quiescent/small ELM H-mode shots (Topic 5,6, 18)
% 		\item Shortly after this meeting we will organize
%                   a follow-up meeting to reconcile ideas
%                   from this discussion (date not fixed yet)
% 		\item All information will be gathered on the wiki
%                 \item Other channels for discussion/sharing. e.g. Slack
%                   (mst1-topic21.slack.com), Github for code sharing, \ldots
% 		\item We aim to arrive to a proper shared database of
%                   filaments between the machines, where properties
%                   will be obtained using agreed approaches so that a
%                   cross-machine comparison paper could at the end be
%                   finalized at a certain point		
% 	\end{itemize}
% \end{frame}

% \begin{frame}{Discussion agenda}
% 	\begin{enumerate}
% 		\item Priorities. These are our personal ideas. Do we agree? 
% 		\item \underline{Common measurement techniques}. Filament
%                   properties, $\Lambda_{div}$ estimate and location,
%                   Neutrals, packing fraction, \ldots 
%  	\end{enumerate}
% \end{frame}

\end{document}

>>>>

\begin{frame}{LSN \textit{vs} Double null on TCV}
%  \begin{columns}
%    \begin{column}{0.5\textwidth}
      \centering{\includegraphics<1>[width=.6\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesLSN-DN}}
      \centering{\includegraphics<2>[width=.8\textwidth]{../../Experiments/TCV/analysis/pdfbox/DNRadiation_58623}}
      \centering{\includegraphics<3>[width=.8\textwidth]{../../Experiments/TCV/analysis/pdfbox/DNRadiation_58624}}
      \centering{\includegraphics<4>[width=.8\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeLSN-DN}}
%    \end{column}
%    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \item<1|only@1> Comparing similar L-Mode density ramp at same
          current in LSN and DN with ion $\mathbf{B}\times\nabla B$
          pointing towards the floor. Lower ion flux to lower target
          observed in DN and profiles before rollover seem more broad
          in LSN. After rollover the profiles are actually similar
      \item<2|only@2>  From bolometry we can observe an
          unbalanced movement of the radiation front suggesting a non
          perfectly balanced DN
      \item<3|only@3> This is confirmed at higher current where the
        more active X-point is the upper one with a consequent higher
        radiation from bolometry chords
      \item<4|only@4> No clear difference in blob size but needs
        further investigation  
      \end{itemize}
%    \end{column}
%  \end{columns}
\end{frame}

@@

\begin{frame}{Cross-machine: different divertor geometry}
  \begin{columns}
    \begin{column}{0.5\textwidth}
  \includegraphics[width=\textwidth]{../generalFigures/Divertors}
\end{column}
\begin{column}{0.5\textwidth}
  \begin{itemize}
    \item Cross-machine experiments (including comparison with
      possible JET experiment) could help to disentangle how divertor
      geometry influence upstream profiles in term of neutral
      compression and recycling
    \item \alert{f.x. Vertical target on JET and AUG has very
        different behavior in terms of shoulder formation}
    \end{itemize}
  \end{column}
\end{columns}
\end{frame}

\begin{frame}{Program for 2018: AUG}
  \begin{itemize}
     \item X-point manipulator (NPH ?) simultaneously with MEM
     \item X-point vertical shift in order to have SP at different
	vertical height at the target. \alert{We will observe similar
          observation as obtained in JET when moving from horizontal
          to vertical target?}
     \item DN discharges. With slow movement of the second X-point into the vessel
	to be performed at constant power/density where shoulder
        alreay exists. \alert{This is mandatory to complement the
          information obtained on TCV}
     \item USN with midplane/X-point manipulator to monitor the
       upstream SOL 
     \item Heat load
\end{itemize}
 \end{frame}
 \begin{frame}{MST2-NPH}
   \begin{columns}
     \begin{column}{0.5\textwidth}
       \centering{\includegraphics[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/NPH_2018}}
     \end{column}
     \begin{column}{0.5\textwidth}
       \begin{itemize}
         \item MST2 founded project for the realization of a New Probe
           Head (NPH) (C. Ionita,  B. Schneider \textit{et al})
         \item Simultaneous information on Ion temperature (2 RFAs),
           Plasma potential and electron temperature (Emissive probe
           coupled with floating potential) and magnetic fluctuations
           from 2 3-axial magnetic pick up coil
         \item Potentially tested on TCV beginning of 2018 and then
           moved to other MST1 devices
       \end{itemize}
     \end{column}
   \end{columns}
 \end{frame}

@@

\begin{frame}{Code requirements}
  \begin{itemize}
    \item Dedicated simulations with first principles codes (GBS,
      HESEL)
    \item Check if trends can be reproduced
    \item potential input for future experiments regarding role of
        f.x. neutrals and recycling
  \end{itemize}
\end{frame}
\end{document}
